---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# Solving and simulating a class of LRE models {-}

This package solves for the recursive representation of the stable solution to a system of linear difference equations. The package contains formulas for dealing with both the autonomous LRE and LRE with an AR element and the associated exogenous shocks.

Specifically, included are:
1) The formulas that give the decision and motion rules for a dynamic system as per Blanchard and Kahn, Klein. With formulas lre_auto for the autonomous case and lre_ar for the AR case.

For the autonomous LRE, Inputs are two square matrices E and A and a natural number n where E and A are the coefficient matrices of the difference equation $Ex_{t+1} = Ax_t$ 

For the AR LRE, inputs are the previously defined matrices E and A in addition to a matrix B and $\Phi$ that satisfy the following system

$Ex_{t+1} = Ax_t + Bu_t \\ u_{t+1} = \Phi u_t + e_t$

2) Simulation formulas that should also provide the impulse response of the system to an exogenous shock to examine the evolution of the dynamic system.

To install run:

```{r, eval = FALSE}
devtools::install_github("nuritovbek/lrem")
```
To use the package, call the required lre function with the coefficient matrices of your model and a number of predetermined variables in n: e.g. 

```{r, eval=F}
library(lrem)
sim <- lre_auto(A, E, n)
```

And then iterate the decision and motion rules by running

```{r, eval = F}
out <- simulate_no_shock(sim[[1]], sim[[2]], x0, t)
```


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

